\documentclass{my_cv}
 
\begin{document}
 \pagenumbering{gobble} 

\name{CJ Boake}
 \vspace{1mm}
\websites{cjboake.com \& github.com/cjboake}
 \vspace{1mm}
\contact{3012 W De Leon \#14}{Tampa}{FL 33609}{cjboake@me.com}{(727)656--9100}

\section{Technologies}
 \begin{tabular}{l l l l l l l}
    C & Java & Javascript & Spring & x86 Assembly & SQL & CI/CD\\
    REST & Unix & \LaTeX{} & Git & Apache Tomcat & TeamCity & Jenkins
 \end{tabular}
 
\section{Work}
 \datedsubsection{Software Engineer I, Express Scripts Int.}{April 2017--June 2018}
  \datesubsection{\sc{edi \& transaction processing}}
   \workitemsfive{Saved over \$10k/year in developer resources with automated Spring Boot error monitor 
        that eliminated the need for corrective action from developers.}
        {Built a client and business-facing Portal extension using Java Servlets/JSP allowing internal and external users to update data and statuses.} 
        {Performed server updates and manual releases of new code on both Microsoft and Linux environments.} 
        {Implemented application-wide security patches for Cross-Site Scripting, SQL injection, forced browsing, and other attacks.}
        {Legacy environments ran Resin \& Apache servers, servlets, Spring Boot, Spring MVC, JQuery and Handlebars
        Javascript frameworks, and HTML/CSS frontends on JSP's.}
  \datesubsection{\sc{new internal portal}}
   \workitem{Wrote persistence layer micro-services to serve data to React.js frontend from SQL Server andMySQL databases,
        and to coordinate with a Stratus mainframe. Persistence was implemented using Spring JPA.}
        {All development took place using Agile practices on a schedule of two-week sprints.}

\datedsubsection{Sofware Developer, NetDirector LLC}{October 2018--July 2019}
 \datesubsection{\sc{Document Transformation \& GUI Interface}}
  \workitemsfive{Maintained Java application that performed document transformation on varying XML mappings into standard forms
     so that clients could process documents regardless of the sender's formatting.}
    {Wrote XML/JSON conversion web service connector to allow clients to flexibly communicate regardless of data type.}
    {Began design and rewrite of Adobe Flash GUI interface into an Angular.js front end communicating with Spring Boot web services.} 
    {Implemented monthly reporting jobs using Java JMS to organization transaction data into Excel spreadsheets in order to alleviate
    analysts of manual data collection tasks.}
    {Wrote Python scripting tools for business analysts to reformat spreadsheets and organize relevant data on the fly, during client communications.}

\section{Projects}
 \datesubsection{C Compiler, \sc{cjcc}}
  \workite{C compiler for the x86\_64 architecture written without the use of any pre-made Lexer/Parser Generator tools 
    or libraries. (Under development)}

\section{Education}
 \datedsubsection{University of Tampa}{2011--2016}
    B.A. Writing, Poetry Focus

\end{document} 
